---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r badges, echo = FALSE}
badge_stars <- function(color = "green", url = NULL, cookie = Sys.getenv("ADVENT_COOKIE")) {
  
  req <- httr::GET(glue::glue('https://adventofcode.com/'),
                   httr::add_headers(.headers = c(
                     "user-agent" = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_15_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/86.0.4240.198 Safari/537.36",
                     "cookie" = paste0("session=", cookie)
                   )))
  
  
  #parsed <- httr::content(req, as = "text")
  
  parsed <- xml2::read_html(req)
  
  stars <- rvest::html_node(parsed, ".user")
  
  star_text <- rvest::html_text(stars)
  
  
  
  badge <- paste0("![](https://img.shields.io/badge/", "star count", "-", star_text, "-", color, ".svg)")
  
  if (is.null(url))
    return(badge)
  
  paste0("[", badge, "](", url, ")")
}
```

### adventofcode2020

<!-- badges: start -->
`r badge_stars("10", "yellow")`
<!-- badges: end -->

If you are finding this, this is my personal repo for the 2020 Advent of Code challenge. I am using this to practice algorithmic thinking, branch out and write more code in Julia, and to just have fun. Feel free to ping me if you have questions!


### Star badges

I am also using this repo as an opportunity to test out adding custom repo badges that scrape a user's star count and create a badge out of it. You can see an example at the top of this page. 
